Addition and removal energies of circular quantum dots

### 2017-09-06 Manuscript/paper.tex
Mention dynamical and static correlations

There is great amount of flexibility in the application of many-body methods.  The approaches we use are shown in Fig.\ \ref{fig:methods}.  Applying the methods in this order maximizes the benefits of each method: HF acts as an initial, crude procedure to ``soften'' the Hamiltonian, followed by IM-SRG or CC to refine the ground state energy, and then finally QDPT or EOM to refine the addition and removal energies.

>>>>

There is significant flexibility in the application of many-body methods.  The approaches we use are shown in Fig.\ \ref{fig:methods}.  Applying the methods in this order maximizes the benefits of each method: HF acts as an initial, crude procedure to ``soften'' the Hamiltonian, followed by IM-SRG or CC to refine the ground state energy, and then finally QDPT or EOM to refine the addition and removal energies.  We expect single-reference IM-SRG and CC to recover a substantial part of the dynamical correlations, while QDPT and EOM help account for static correlations.
